Mining of Keystroke and Mouse Dynamics to Increase the Engagement of Students with Programming Assignments

### 2018-04-21 paper.tex
Reviewed changes
Explaining the GA algorithm

As part of the data mining process a canonical genetic algorithm was used for feature
selection with the parameters used shown in Table \ref{tab_ga}. These
parameters were set heuristically and were the same for selecting the
features of all classification algorithms. The population size was changed
mainly because the feature vector is real-valued and is more computationally demanding.  
% Mario check this - JJ
% OK, added another sentence - Mario 
In the end, the subset for the frustration classifier includes only 11 features, and 
the subset for the boredom classifier consists of only 13 features.

@@

Table \ref{tab_perf_flow} shows the performance for the additional classifiers
evaluated specifically for the Flow/engaged affective state. The goal was to
increase the performance achieved earlier. Again a ten-
fold cross-validation was conducted. In this case, instead of using an
evolutionary algorithm to optimize feature selection, it was used for 
optimizing a weight vector. 
      The feature-weight vector assigned a weight to each one of the
      features, and the parameters that have been used in the
      evolutionary algorithm are shown in Table \ref{tab_ga_w}.
      % The
% parameters used for the evolutionary optimization algorithm are the following:
% Population size = 10, generations = 30, selection = tournament, tournament size = 0.25 (fraction of the population),  initialize probability = 0.5,  mutation
%       probability = 1/number of attributes,  crossover probability =
%       0.5.
      % Please Mario check these parameters and how they have put to
      % the table; I don't know what's the "initialization
      % probability" - JJ

>>>>

As part of the data mining process a canonical genetic algorithm was used for feature
selection with the parameters used shown in Table \ref{tab_ga}. These
parameters were set heuristically and were the same for selecting the
features of all classification algorithms. The population size was changed
mainly because some of the algorithms are more computationally demanding. The
genetic algorithm is included as a RapidMiner operator. In the algorithm, each
individual consists of a binary list indicating if a feature will be used or
not. The mutation operator simply changes the switch with the probability
indicated in the mutation-probability parameter.  When the population is
initialized each switch has 0.5 probability of being "on".

% Mario check this - JJ
% OK, added another sentence - Mario 
% Added a mini explanation of the GA. - Mario

In the end, the subset for the frustration classifier includes only 11 features, and 
the subset for the boredom classifier consists of only 13 features.

@@

Table \ref{tab_perf_flow} shows the performance for the additional classifiers
evaluated specifically for the Flow/engaged affective state. The goal was to
increase the performance achieved earlier. Again a ten-
fold cross-validation was conducted. Again, an evolutionary algorithm was used for feature with the parameters shown in Table \ref{tab_ga_w}.
      % The
% parameters used for the evolutionary optimization algorithm are the following:
% Population size = 10, generations = 30, selection = tournament, tournament size = 0.25 (fraction of the population),  initialize probability = 0.5,  mutation
%       probability = 1/number of attributes,  crossover probability =
%       0.5.
      % Please Mario check these parameters and how they have put to
      % the table; I don't know what's the "initialization
      % probability" - JJ
      % Is the probability a feature has to be "on" (used by the algorithm)
      % initially.
